Homicide Increases in the COVID-19 Era

### 2025-02-20 Draft1.qmd
Added viz

```{r}
library(sf)
library(tidygeocoder)
zcta <- read_sf(dsn = "cb_2020_us_zcta520_500k", layer = "cb_2020_us_zcta520_500k")
LA_zctas <- read.csv("Raw_Data/zctas.csv") #obtained using zipcodeR::search_city("Los Angeles", "CA") and then checking which zip codes are also ZCTAs

@@

plot(st_geometry(zcta_with_data), 
     col = brewer.pal(9, "Blues")[as.numeric(cut(zcta_with_data$S1903_C03_001E, 
                                                 breaks = 9))], 
     border = 'grey', 
     axes = TRUE, 
     main = "Median Household Income by ", 
     cex.main = 1.5)
```

>>>>

```{r}
library(sf)
library(tidygeocoder)
library(tidyverse)
library(RColorBrewer)

zcta <- read_sf(dsn = "Raw_Data/cb_2020_us_zcta520_500k", layer = "cb_2020_us_zcta520_500k")
LA_zctas <- read.csv("Raw_Data/zctas.csv") #obtained using zipcodeR::search_city("Los Angeles", "CA") and then checking which zip codes are also ZCTAs

@@

zcta_no_NAs <- zcta_with_data %>% filter(!is.na(S1903_C03_001E))

plot(st_geometry(zcta_with_data), 
     col = brewer.pal(9, "Blues")[as.numeric(cut(zcta_with_data$S1903_C03_001E, 
                                                 breaks = 9))], 
     border = 'grey', 
     axes = TRUE, 
     main = "Median Household Income by Year and Zip Code", 
     cex.main = 1.5)
```

# Plot 6 - Frequency of Top 10 Crimes
